InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-25 paper.tex
Write section about BLOOM

>>>>

Another generative model for text is \textbf{BLOOM}. This huge 176 billion parameter big model was published in 2023 and is openly available. The model is multilingual and was built in a decentralized manner by many different contributors. Hundreds of researchers helped with the development of the architecture and tokenizer. The final model was trained on the Jean Zay supercomputer. It is built with a decoder-only architecture and used the ROOTS corpus dataset for training. \cite{workshop2023bloom}
